Optimal forward modeling of gravitational fields using tesseroids with adaptive discretization

### 2014-08-25 manuscript.tex
Added a bit about the tesseroid dimensions

\begin{equation}
    V(r,\phi,\lambda) = G \rho
        \int\limits_{\lambda_1}^{\lambda_2}
        \int\limits_{\phi_1}^{\phi_2}
        \int\limits_{r_1}^{r_2}
        \frac{1}{\ell} \kappa  dr' d\phi' d\lambda',
    \label{eq:tesspot}
\end{equation}
\begin{equation}
    g_{\alpha}(r,\phi,\lambda) = G \rho
        \int\limits_{\lambda_1}^{\lambda_2}
        \int\limits_{\phi_1}^{\phi_2}
        \int\limits_{r_1}^{r_2}
        \frac{\Delta_{\alpha}}{\ell^3} \kappa dr' d\phi' d\lambda'
        \ \ \ \alpha \in \{x,y,z\},
    \label{eq:tessgrav}
\end{equation}

@@

\noindent
in which
$(\phi, \lambda, r)$ are
the latitude, longitude, and radius
coordinates of computation point P (Fig.~\ref{fig:tesseroid}),
$\alpha,\beta \in \{x,y,z\}$
are the local coordinate system of point P,
and

@@

We have developed a modified version
of the recursive division algorithm of \citet{Li2011}.
We fix the number of nodes in the GLQ
$N^\lambda=N^\phi=N^r=2$
so that the distance between nodes
in the radial, longitudinal, and latitudinal directions
are approximately the dimensions of the tesseroid
\citep{Wild-Pfeiffer2008}.
We define the distance $d$ as
the Cartesian distance between
the computation point $P$
and the center of the top face of the tesseroid
(Fig.~\ref{fig:ratio}a).

@@

\begin{eqnarray*}
    L_r &=& r_2 - r_1,\\
    L_\phi &=& R(\phi_2 - \phi_1),\\
    L_\lambda &=& R(\lambda_2 - \lambda_1),
\end{eqnarray*}

\noindent
where $R$ is the mean Earth radius
and the longitudes and latitudes are given in radians.

>>>>

\begin{equation}
    V(r,\phi,\lambda) = G \rho
        \int\limits_{\lambda_1}^{\lambda_2}
        \int\limits_{\phi_1}^{\phi_2}
        \int\limits_{r_1}^{r_2}
        \frac{1}{\ell} \kappa  dr' d\phi' d\lambda',
    \label{eq:tesspot}
\end{equation}

\begin{equation}
    g_{\alpha}(r,\phi,\lambda) = G \rho
        \int\limits_{\lambda_1}^{\lambda_2}
        \int\limits_{\phi_1}^{\phi_2}
        \int\limits_{r_1}^{r_2}
        \frac{\Delta_{\alpha}}{\ell^3} \kappa dr' d\phi' d\lambda'
        \ \ \ \alpha \in \{x,y,z\},
    \label{eq:tessgrav}
\end{equation}

@@

\noindent
in which
$G$ is the gravitational constant,
$(\phi, \lambda, r)$ are
the latitude, longitude, and radius
coordinates of computation point P (Fig.~\ref{fig:tesseroid}),
$\alpha,\beta \in \{x,y,z\}$
are the local coordinate system of point P,
and

@@

We have developed a modified version
of the recursive division algorithm proposed by \citet{Li2011}.
One of the modifications made is that
we fix the number of GLQ nodes as
$N^\lambda=N^\phi=N^r=2$.
In this way, the distances between adjacent nodes
are approximately the dimensions of the tesseroid
\citep[see][]{Wild-Pfeiffer2008}.
Thus, we may use the tesseroid dimensions
as proxies for the distance between nodes.
We define the dimensions of a tesseroid
in the radial, latitudinal, longitudinal directions, respectively,
as

\begin{eqnarray}
    L_r &=& r_2 - r_1,\\
    L_\phi &=& R(\phi_2 - \phi_1),\\
    L_\lambda &=& R(\lambda_2 - \lambda_1),
\end{eqnarray}

\noindent
where $R=6378137\ m$ is the mean Earth radius
and the longitudes and latitudes are given in radians.

We define the distance $d$ as
the Cartesian distance between
the computation point $P$
and the center of the top face of the tesseroid
(Fig.~\ref{fig:ratio}a).

@@
